---
title: "Challenge #366 Word Funnel 1"
author: "Derek"
date: "October 1, 2018"
output: html_document
---

```{r setup, include=FALSE}
library(magrittr)
library(microbenchmark)

knitr::opts_chunk$set(echo = TRUE)
options(stringsAsFactors = FALSE)
```

Working on the reddit daily programmer challenge: https://www.reddit.com/r/dailyprogrammer/comments/98ufvz/20180820_challenge_366_easy_word_funnel_1

## Challenge

> Given two strings of letters, determine whether the second can be made from the first by removing one letter. The remaining letters must stay in the same order.

```
funnel("leave", "eave") => true
funnel("reset", "rest") => true
funnel("dragoon", "dragon") => true
funnel("eave", "leave") => false
funnel("sleet", "lets") => false
funnel("skiff", "ski") => false
```

```{r}
challenge.set <- data.frame(target = c("leave", "reset", "dragoon", "eave", "sleet", "skiff"),
                            test = c("eave", "rest", "dragon", "leave", "lets", "ski"))
```


### Brute force

Since it's just removing one letter, I can create all possible one letter combinations, and see if the given string exists in that set

```{r}
funnel <- function(target, test){
  
  target.chr <- strsplit(target, "*") %>% unlist
  
  target.set <- sapply(seq_along(target.chr), 
                       function(x) {
    paste(target.chr[-x], collapse = "")
    }
    )
  
  return(test %in% target.set)
  
}
```


```{r}
apply(challenge.set, 1, function(x){
  funnel(target = x[1], test = x[2])
})
```

```{r}
microbenchmark(
  apply(challenge.set, 1, function(x){funnel(target = x[1], test = x[2])})
)
```


## Bonus

Given a string, find all words from the enable1 word list that can be made by removing one letter from the string. If there are two possible letters you can remove to make the same word, only count it once. Ordering of the output words doesn't matter.

```{r}
enable1 <- read.csv("https://raw.githubusercontent.com/dolph/dictionary/master/enable1.txt", header = FALSE)[, 1]
```

```{r}
bonus <- function(wordlist, query){
  query.chr <- strsplit(query, "*") %>% unlist
  
  query.set <- sapply(seq_along(query.chr), 
                       function(x) {
    paste(query.chr[-x], collapse = "")
    }
    )
  
  return(wordlist[wordlist %in% query.set])
}
```


```{r}
bonus(enable1, "dragoon")
bonus(enable1, "boats")
bonus(enable1, "affidavit")
```

```{r}
microbenchmark(bonus(enable1, "dragoon"),
               bonus(enable1, "boats"),
               bonus(enable1, "affidavit"))
```


## bonus 2

>Given an input word from enable1, the largest number of words that can be returned from `bonus(word)` is 5. One such input is "boats". There are 28 such inputs in total. Find them all.

>Ideally you can do this without comparing every word in the list to every other word in the list. A good time is around a second. Possibly more or less, depending on your language and platform of choice - Python will be slower and C will be faster. The point is not to hit any specific run time, just to be much faster than checking every pair of words.


### ugly

brute force way is to just run `bonus` on the entire list, and then find the number of values returned for each query

```{r, eval = FALSE}
catch <- sapply(enable1, function(x){
  bonus(enable1, x) %>% length
})

catch[catch == 5]
```


### Thought


One thing is that we can reduce the amouont of input. Four letter words can have at most four matches, so we can exclude those

```{r}
length(enable1)
enable5 <- enable1[ nchar(enable1) > 4]
length(enable5)
```


Dang, that cut down the search space down to only `r length(enable5) / length(enable1)` of what it was. 

-----------


One thing I noticed is that for five letter words, the only search space is four letter words, for six letter, five. 

So, steps to do this search would be:

- sort words
- split into lists based on number of char
- some kind of function to go through a list of n-letter words, and search for n-1-letter words

```{r}
max(sapply(enable5, nchar))
```

ok, so the max number is 28. Also it ran pretty fast so I think I can just use nchar(x) == n, and go through the different n's


```{r}
nletters.ls <- lapply(4:28, function(n){
  return( enable1[nchar(enable1) == n ])
})

names(nletters.ls) <- 4:28
```

Here we go:

```{r}
time1 <- Sys.time()
fivefunnel <- sapply(2:25, function(n){
  wordlen <- sapply(nletters.ls[[n]], function(x){ 
         bonus(wordlist = nletters.ls[[n-1]], query = x) %>% 
      length
  }
  )
  
  keeps <- nletters.ls[[n]][wordlen == 5]
  return(keeps)
})
time2 <- Sys.time()

time2- time1

# Time difference of 2.657189 mins

fivefunnel %>% unlist %>% length

fivefunnel %>% unlist
```

