---
title: '#366 Word Funnel 2'
author: "Derek"
date: "October 3, 2018"
output: html_document
---

```{r setup, include=FALSE}
library(magrittr)
library(microbenchmark)

knitr::opts_chunk$set(echo = TRUE)
options(stringsAsFactors = FALSE)
```

## Challenge


> A word funnel is a series of words formed by removing one letter at a time from a starting word, keeping the remaining letters in order. For the purpose of this challenge, a word is defined as an entry in the [enable1 word list](https://raw.githubusercontent.com/dolph/dictionary/master/enable1.txt). An example of a word funnel is:

```
gnash => gash => ash => ah
```

> This word funnel has length 4, because there are 4 words in it.

> Given a word, determine the length of the longest word funnel that it starts. You may optionally also return the funnel itself (or any funnel tied for the longest, in the case of a tie).

**Examples**

```
funnel2("gnash") => 4
funnel2("princesses") => 9
funnel2("turntables") => 5
funnel2("implosive") => 1
funnel2("programmer") => 2
```

### solution

```{r}
library(data.tree)
```


```{r}
enable1 <- read.csv("https://raw.githubusercontent.com/dolph/dictionary/master/enable1.txt", header = FALSE)[, 1]
```


```{r}
# making a reduced search space list
word.list <- split(enable1, nchar(enable1))
```


```{r}
# rewriting the wordfunnel1-bonus function to make it easier to use
FindChildWords <- function(query, wordlist = enable1){
  query.chr <- strsplit(query, "*") %>% unlist
  
  query.set <- sapply(seq_along(query.chr), 
                       function(x) {
    paste(query.chr[-x], collapse = "")
    }
    )
  
  # ret.list <- as.list(wordlist[wordlist %in% query.set])
  # names(ret.list) <- ret.list %>% unlist
  
  return(wordlist[wordlist %in% query.set])
}


BuildWordTree <- function(parent){
  # - check if parent is Node, if not, make it so
  if( typeof(parent) != "environment") parent <- Node$new(parent)

  
  ################
  # create child nodes
  child.words <- FindChildWords(parent$Get("name"), word.list[[nchar(parent$Get("name")) - 2]])
  
  # if no child words found, we're done here.
  if(length(child.words) == 0){
    return(parent)
  }
  # otherwise, let's add child nodes
  for (word in child.words) child <- parent$AddChild(word)
  
  ##################
  # recurse into child nodes and run function as long as nchar > 2
  if(parent$children[[1]]$Get("name") %>% nchar > 2){
    for(i in seq_along(child.words)) BuildWordTree(parent = parent$children[[i]])
  }
  
  # - return parent Node
  return(parent)
}
```

```{r}
microbenchmark(BuildWordTree("princesses"), times = 20)
```

Speed looks acceptable.

```{r}
funnel2 <- function(word){
  word.tree <- BuildWordTree(word)
  
  word.tree$Get("level") %>% max
}
```


```{r}
test.cases <- c("gnash", "princesses", "turntables", "implosive", "programmer")
```

```{r}
microbenchmark(
  sapply(test.cases, funnel2),
  times = 20)
```

```{r}
sapply(test.cases, funnel2)
```


## Session info

```{r}
system("lscpu", intern = TRUE) %>% cat(sep = "\n")
sessionInfo()
```


-------------

## work

loading in the enable1 wordlist

```{r}
enable1 <- read.csv("https://raw.githubusercontent.com/dolph/dictionary/master/enable1.txt", header = FALSE)[, 1]
```

My first thought is to take the function that I wrote in "Word Funnel 1", apply that to the word, and then recursively apply that to the output until I am down to one letter.

```{r}
wf1.bonus <- function(wordlist, query){
  query.chr <- strsplit(query, "*") %>% unlist
  
  query.set <- sapply(seq_along(query.chr), 
                       function(x) {
    paste(query.chr[-x], collapse = "")
    }
    )
  
  return(wordlist[wordlist %in% query.set])
}
```


For example, following `boats -> bats`

```{r}
wf1.bonus(enable1, "boats")
wf1.bonus(enable1, "bats")
wf1.bonus(enable1, "bat")
wf1.bonus(enable1, "ba")
```

Hmm, since `a` didn't turn up, are there single letter words?

```{r}
enable1 %>% nchar %>% table
```

nope.

Next thing is how to store this information? 

I could go through each tree and record the length of the largest chain. Some kind of logic of:

- run bonus to get the list of words
- run bonus on each result and keep track of which one(s) return results
- store the ones that had results, and their results
- repeat on the new results

I think the next step is how to store these data -- my mind goes towards some kind of tree structure. Let's see if I can implement that in R lists 

```{r}
# I'll need to rewrite the function to return a named list
wf2 <- function(wordlist, query){
  query.chr <- strsplit(query, "*") %>% unlist
  
  query.set <- sapply(seq_along(query.chr), 
                       function(x) {
    paste(query.chr[-x], collapse = "")
    }
    )
  
  ret.list <- as.list(wordlist[wordlist %in% query.set])
  names(ret.list) <- ret.list %>% unlist
  
  return(ret.list)
}

boat.tree <- wf2(enable1, "boats")

round1 <- lapply(boat.tree, function(x) wf2(enable1, x))
round1
```


Well, that's a start. I'm not sure how I would transverse this structure .... 

#### data.tree

```{r}
library(data.tree)
```


Ok, let's try to recreate what I was doing with the lists, except with data.tree.

This is going to be harder than I expected because data.tree uses R6 classes. 

```{r}
# rewriting the wordfunnel1-bonus function to make it easier to use
FindChildWords <- function(query, wordlist = enable1){
  query.chr <- strsplit(query, "*") %>% unlist
  
  query.set <- sapply(seq_along(query.chr), 
                       function(x) {
    paste(query.chr[-x], collapse = "")
    }
    )
  
  # ret.list <- as.list(wordlist[wordlist %in% query.set])
  # names(ret.list) <- ret.list %>% unlist
  
  return(wordlist[wordlist %in% query.set])
}

```



```{r}
# starting the tree with a root node
(boats.tree <- Node$new("boats"))

# let's add the results of the first word funnel iteration
FindChildWords("boats")
FindChildWords("boats") %>% sapply(., FUN = function(x) boats.tree$AddChild(x)) %>% invisible()
boats.tree

```


so I guess that did something ... but it doesn't feel right. And I'm unsure how I would tell R to 'do that for every child node' ...

```{r}
boats.tree$Get("name", filterFun = isLeaf)
```


In reading the vignette(s) / internet, it looks like I should go about this by making a function that constructs the tree recursively ....

In general the steps are:

- check if parent is Node, if not, make it so
- create child nodes
- recurse into child nodes and run function as long as nchar > 2
- return parent Node

```{r}
# making a reduced search space list
word.list <- split(enable1, nchar(enable1))
```


```{r}
BuildWordTree <- function(parent){
  # - check if parent is Node, if not, make it so
  if( typeof(parent) != "environment") parent <- Node$new(parent)

  
  ################
  # create child nodes
  child.words <- FindChildWords(parent$Get("name"), word.list[[nchar(parent$Get("name")) - 2]])
  
  # if no child words found, we're done here.
  if(length(child.words) == 0){
    return(parent)
  }
  # otherwise, let's add child nodes
  for (word in child.words) child <- parent$AddChild(word)
  
  ##################
  # recurse into child nodes and run function as long as nchar > 2
  if(parent$children[[1]]$Get("name") %>% nchar > 2){
    for(i in seq_along(child.words)) BuildWordTree(parent = parent$children[[i]])
  }
  
  # - return parent Node
  return(parent)
}
```

```{r}
boat.tree <- BuildWordTree("boats")
boat.tree

princesses.tree <- BuildWordTree("princesses")

microbenchmark(BuildWordTree("princesses"), times = 20)
```

That speed looks promising? 

Next is how do I find the longest branch of the tree returned? 

```{r}
boat.tree$Get("level") %>% max
```


```{r}
funnel2 <- function(word){
  word.tree <- BuildWordTree(word)
  
  word.tree$Get("level") %>% max
}
```

funnel2("gnash") => 4
funnel2("princesses") => 9
funnel2("turntables") => 5
funnel2("implosive") => 1
funnel2("programmer") => 2

```{r}
test.cases <- c("gnash", "princesses", "turntables", "implosive", "programmer")
```

```{r}
sapply(test.cases, funnel2)
```




-------------------------------------


## Bonus 1

> Find the one word in the word list that starts a funnel of length 10.



### Work

Is it tenable to just step upwards until I find a word that has a funnel of length 10?
```{r}
# let's see how long it takes to run 20 12-letter words
startt <- Sys.time()
catch <-  word.list[[11]] %>% sapply(. , function(x) funnel2(x))
endt <- Sys.time()

endt - startt
# Time difference of 24.5908 secs
```


## Bonus 2

> For this bonus, you are allowed to remove more than one letter in a single step of the word funnel. For instance, you may step from sideboard to sidebar by removing the o and the final d in a single step. With this modified rule, it's possible to get a funnel of length 12:

```
preformationists =>
preformationist =>
preformations =>
reformations =>
reformation =>
formation =>
oration =>
ration =>
ratio =>
rato =>
rat =>
at
```

`preformationists` is one of six words that begin a modified funnel of length 12. Find the other five words.


### work


Something worth considering is building trees top-down vs. bottom up -- starting with big words and finding those that are in them, vs starting with the smallest words and finding which words could contain them. 

I think bottom up would work the best, just because I can think of a way to grep for them:

searching for parents of "bat"

```
grep("*bat", fourletterwords)
grep("b*at", fourletterwords)
grep("ba*t", fourletterwords)
grep("bat*", fourletterwords)
```

As I got I could store the length of the longest branch.

It would be neat if I could also store the longest branch to see what the words are. 